---
title: "Getting Started with CTBN-Multimorbidity"
output:
  rmarkdown::html_vignette:
    toc: true
    toc_depth: 2
vignette: >
  %\VignetteIndexEntry{Getting Started with CTBN-Multimorbidity}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r setup, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment  = "#>",
  fig.width  = 6,
  fig.height = 4
)
```

# Overview

This vignette walks through fitting a Continuous-Time Bayesian Network
(CTBN) with order-dependent structured shrinkage priors to a small
synthetic multimorbidity dataset. The methodology is described in full in
the accompanying paper:

> Olaniran et al. (2026). *Continuous-Time Bayesian Networks with
> Structured Shrinkage Priors for Modelling Multimorbidity Trajectories
> in Large-Scale Electronic Health Records.*

We use the **fast MAP estimator** (`ctbn_map_fast()`) here because it
runs in seconds on the small synthetic dataset; the full Stan path
(`ctbn_fit()`) has an identical interface.

# 1. Simulate a small CTBN trajectory

```{r sim, eval = FALSE}
# Source the library code (these are stand-alone files, not yet a package)
source(file.path("..", "R", "ctbn_map_fast.R"))
source(file.path("..", "scripts", "simulation", "01_map_simulation.R"))

# Generate a small dataset (N = 1000 patients, T = 10 years)
sim    <- generate_dataset(n = 1000, seed = 2026)
DT_wide <- prepare_wide(sim)

# Inspect
str(DT_wide)
```

# 2. Fit the spike-and-slab CTBN

```{r fit, eval = FALSE}
fit <- ctbn_map_fast(
  DT_wide,
  max_order = 2L,           # P = 2 — main effects + pairwise interactions
  prior     = "spike_slab", # recommended prior
  theta     = 1.0,          # order penalty
  pi0       = 0.10,         # base inclusion probability
  verbose   = TRUE
)
```

The returned object is a list with one slot per target condition, each
containing:

* `beta_hat`, `gamma_hat`, `beta0_hat` — posterior MAP estimates
* `se_beta`, `se_gamma`             — Laplace standard errors
* `pip_hat`                          — exact PIPs (spike-and-slab) or
                                       pseudo-PIPs (continuous priors)
* `loglik`, `aic`, `bic`            — diagnostics

# 3. Extract the inferred network

```{r summary, eval = FALSE}
# Print a network summary at PIP threshold 0.5
summary(fit, pip_threshold = 0.5)

# Edges with PIP >= 0.95 (paper-style "highly supported")
edges <- compute_selection_stats(
  beta_hat = fit$IHD$beta_hat,
  se_beta  = fit$IHD$se_beta,
  x_orders = fit$IHD$x_orders,
  prior    = "spike_slab",
  pip_threshold = 0.95
)
edges[edges$active, ]
```

# 4. Compute the 5-year cumulative incidence function

```{r ci, eval = FALSE}
# Reference patient with all parent conditions absent
ref_patient <- DT_wide[1, ]
ref_patient[, names(DT_wide)[grep("^X_", names(DT_wide))] := 0L]

F_m <- compute_F_m(
  fit         = fit,
  target      = "IHD",
  patient_dt  = ref_patient,
  tau         = 5,                  # 5-year horizon
  zbar        = NULL                # population-average covariate vector
)
F_m
```

# 5. Cross-validated predictive performance

For a 5-fold patient-level cross-validation across all four priors,
P ∈ {1, 2} and θ ∈ {0.5, 1, 2}:

```{r cv, eval = FALSE}
folds <- make_patient_folds(DT_wide, k = 5, seed = 42)

cv_results <- ctbn_cv_compare(
  DT_wide      = DT_wide,
  folds        = folds,
  priors       = c("spike_slab", "structured", "lasso", "horseshoe"),
  p_grid       = c(1L, 2L),
  theta_grid   = c(0.5, 1.0, 2.0),
  eval_times   = c(1, 2, 5, 7, 10),
  parallel     = TRUE,
  use_map_fast = TRUE                # set to FALSE for full Stan path
)

summarise_cv(cv_results)
plot_tdauc(cv_results)
```

# 6. What's next?

* For the full UK Biobank analysis pipeline, see
  `scripts/ukb_analysis/04_stan_results.R` — the script that produced
  the figures and tables of the paper.
* For the simulation study reported in the paper, see
  `scripts/simulation/03_stan_simulation.R`.
* All output figures and tables are kept under `paper/figures/`,
  `paper/tables/`, and `paper/sim_results/`.
